---
title: "Console Mode"
author: "Eric Starke"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Console Mode}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(easyshiny)
library(shiny)
library(ggplot2)
es_init()
```

## Console mode

There is a console mode in easyshiny, which makes it easier to develop your app. 
It gives you access to the plots, as they would be rendered in the browser and to the input data in tibble form.
To activate this feature you just have to provide a folder with example data to `es_init`.

```{r, eval=FALSE}
es_init(local_folder = 'path/to/sample/data')
```

After that it is possible to access the data and plots from the console.

```{r, results='hidden'}
es_read('bike_buyers.csv', readerId = 'bike_buyers')

testplot <- es_add_output(
  renderPlot,
  {
  ggplot(mpg, aes(cty, hwy)) +
    geom_point()
  }
)
```

A function is returned, which gives the dataframe/plot when called. 
It is also possible to view plots containing input values and using the sample data,
as in this example:

```{r, results='hidden'}
es_read('bike_buyers.csv', readerId = 'bike_buyers')

es_add_input(
  sliderInput,
  tab = 'Bikes',
  box = 'Visualization',
  inputId = "agespan",
  label='choose an agespan:',
  min=0,
  max=90,
  value=c(0,90)
)

income_age_plot <- es_add_output(
  renderPlot,
  {
  ggplot(
    bike_buyers() %>% filter(Age >= input$agespan[1] & Age <= input$agespan[2]),
    aes(x=Age, y=Income)) +
      geom_point() +
      geom_smooth()
  }, 
  tab = 'Bikes', 
  box = 'Visualization'
)
```

The starting values of any input object will be used to create the plot.
